PANCHANGE_analysis

### 2020-11-12 PANCHANGE_analysis.Rmd
updated education/employment sensitivity models

dim(dat.retro_sensitivity)
```
age^2 sensitivity 
Exclude individuals with NA for continuous Age variable
```{r}
dat_age_sensitivity <- dat %>%
  filter(!is.na(Age))
dim(dat_age_sensitivity)
```

Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
```{r subsample for pre-pan sensitivity analysis}
# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_3months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_6months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_9months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
  )

```

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b diff_score prepan}
# Regression coefficients
gad_prepan_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(gad_prepan_model1b_estimates)
gad_prepan_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a sum_score prepan}
# Regression coefficients
gad_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1a_explan_estimates)
gad_prepan_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```
# GAD prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r gad model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

#### Subset of participants 6 months prior to pandemic
```{r gad model1b sum_score prepan - sensitivity 6 months}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

#### Subset of participants 9 months prior to pandemic
```{r gad model1b sum_score prepan - sensitivity 9 months}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```
##KT

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a diff_score retro}
# Regression coefficients
gad_retro_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(gad_retro_model1a_estimates)
gad_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b diff_score retro}
# Regression coefficients
gad_retro_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(gad_retro_model1b_estimates)
gad_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a sum_score retro}
# Regression coefficients
gad_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1a_explan_estimates)
gad_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b sum_score retro}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a diff_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model1a_estimates)
gad_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b diff_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model1b_estimates)
gad_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a sum_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model1a_explan_estimates)
gad_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b sum_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a absolute whole sample}
# Regression coefficients
phq_baseline_model1a_estimates <- model1a.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1a_estimates)
phq_baseline_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b absolute whole sample}
# Regression coefficients
phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1b_estimates)
phq_baseline_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a diff_score prepan}
# Regression coefficients
phq_prepan_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model1a_estimates)
phq_prepan_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b diff_score prepan}
# Regression coefficients
phq_prepan_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model1b_estimates)
phq_prepan_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a sum_score prepan}
# Regression coefficients
phq_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1a_explan_estimates)
phq_prepan_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_explan_estimates)
phq_prepan_model1b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```
# PHQ prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r phq model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(phq_prepan_model1b_explan_estimates)
phq_prepan_model1b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```

#### Subset of participants 6 months prior to pandemic
```{r phq model1b sum_score prepan - sensitivity 6 months}
# Regression coefficients
phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(phq_prepan_model1b_explan_estimates)
phq_prepan_model1b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```

#### Subset of participants 9 months prior to pandemic
```{r phq model1b sum_score prepan - sensitivity 9 months}
# Regression coefficients
phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(phq_prepan_model1b_explan_estimates)
phq_prepan_model1b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a diff_score retro}
# Regression coefficients
phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model1a_estimates)
phq_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b diff_score retro}
# Regression coefficients
phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model1b_estimates)
phq_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a sum_score retro}
# Regression coefficients
phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1a_explan_estimates)
phq_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b sum_score retro}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a diff_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model1a_estimates)
phq_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b diff_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model1b_estimates)
phq_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a sum_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model1a_explan_estimates)
phq_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b sum_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a absolute whole sample}
# Regression coefficients
ocir_baseline_model1a_estimates <- model1a.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1a_estimates)
ocir_baseline_model1a_estimates

>>>>

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b diff_score prepan}
# Regression coefficients
gad_prepan_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(gad_prepan_model1b_estimates)
gad_prepan_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a sum_score prepan}
# Regression coefficients
gad_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1a_explan_estimates)
gad_prepan_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a diff_score retro}
# Regression coefficients
gad_retro_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(gad_retro_model1a_estimates)
gad_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b diff_score retro}
# Regression coefficients
gad_retro_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(gad_retro_model1b_estimates)
gad_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a sum_score retro}
# Regression coefficients
gad_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1a_explan_estimates)
gad_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b sum_score retro}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a diff_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model1a_estimates)
gad_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b diff_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model1b_estimates)
gad_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a sum_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model1a_explan_estimates)
gad_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b sum_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a absolute whole sample}
# Regression coefficients
phq_baseline_model1a_estimates <- model1a.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1a_estimates)
phq_baseline_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b absolute whole sample}
# Regression coefficients
phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1b_estimates)
phq_baseline_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a diff_score prepan}
# Regression coefficients
phq_prepan_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model1a_estimates)
phq_prepan_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b diff_score prepan}
# Regression coefficients
phq_prepan_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model1b_estimates)
phq_prepan_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a sum_score prepan}
# Regression coefficients
phq_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1a_explan_estimates)
phq_prepan_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_explan_estimates)
phq_prepan_model1b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a diff_score retro}
# Regression coefficients
phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model1a_estimates)
phq_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b diff_score retro}
# Regression coefficients
phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model1b_estimates)
phq_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a sum_score retro}
# Regression coefficients
phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1a_explan_estimates)
phq_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b sum_score retro}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a diff_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model1a_estimates)
phq_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b diff_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model1b_estimates)
phq_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a sum_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model1a_explan_estimates)
phq_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b sum_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a absolute whole sample}
# Regression coefficients
ocir_baseline_model1a_estimates <- model1a.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1a_estimates)
ocir_baseline_model1a_estimates
